\begin{zed}
  [PID]
\end{zed}

\begin{zed}
Senal ::= Activate | Suspend | Kill | KillNow
\end{zed}

\begin{zed}
Estado ::= activo | pasivo | muerto
\end{zed}

\begin{zed}
MSG ::= ok | errProcExist | errProcSuscrito | sinCambios | errProcNoExistente
\end{zed}

\begin{schema}{SISTEMA}
  prim: PID\\
  ps: PID \pfun  Estado\\
  suscritos: PID \rel  Senal
\end{schema}

\begin{axdef}
  idle: PID
\end{axdef}

\begin{schema}{SISTEMAInit}
  SISTEMA
\where
  prim = idle\\
  ps = \emptyset\\
  suscritos = \emptyset
\end{schema}

\begin{schema}{SistNuevoProcesoOK}
  \Delta SISTEMA\\
  i?: PID\\
  rep!: MSG
\where
  i? \notin  \dom  ps\\
  prim' = prim\\
  ps' = ps \cup  \{(i? \mapsto  pasivo)\}\\
  suscritos' = suscritos\\
  rep! = ok
\end{schema}

\begin{schema}{SistProcesoExistenteERR}
  \Xi SISTEMA\\
  i?: PID\\
  rep!: MSG
\where
  i? \in  \dom  ps\\
  rep! = errProcExist
\end{schema}

\begin{schema}{SistProcesoNoExistenteERR}
  \Xi SISTEMA\\
  i?: PID\\
  rep!: MSG
\where
  i? \notin  \dom  ps\\
  rep! = errProcNoExistente
\end{schema}

\begin{schema}{SistSuscProcesoOK}
  \Delta SISTEMA\\
  i?: PID\\
  s?: Senal\\
  rep!: MSG
\where
  i? \in  \dom  ps\\
  prim' = prim\\
  ps' = ps\\
  suscritos' = suscritos \cup  \{(i? \mapsto  s?)\}\\
  rep! = ok
\end{schema}

\begin{schema}{SistActivateOK}
  \Delta SISTEMA\\
  rep!: MSG
\where
  \dom  (suscritos \rres  \{Activate\}) \cap  \dom  (ps \rres  \{pasivo\}) \neq  \emptyset\\
  suscritos' = suscritos\\
  ps' = ps \oplus  (\dom  (suscritos \rres  \{Activate\}) \cap  \dom  (ps \rres  \{pasivo\}) \cross  \{activo\})\\
  prim' \in  \dom  (suscritos \rres  \{Activate\}) \cap  \dom  (ps \rres  \{pasivo\})\\
  rep! = ok
\end{schema}

\begin{schema}{SistActivateSC}
  \Xi SISTEMA\\
  rep!: MSG
\where
  \dom  (suscritos \rres  \{Activate\}) \cap  \dom  (ps \rres  \{pasivo\}) = \emptyset\\
  rep! = sinCambios
\end{schema}

\begin{schema}{SistSuspendOK}
  \Delta SISTEMA\\
  rep!: MSG
\where
  \dom  (ps \rres  \{activo\}) \setminus  \dom  (suscritos \rres  \{Suspend\}) \neq  \emptyset\\
  suscritos' = suscritos\\
  ps' = ps \oplus  (\dom  (suscritos \rres  \{Suspend\}) \cap  \dom  (ps \rres  \{activo\}) \cross  \{pasivo\})\\
  prim' \in  \dom  (ps \rres  \{activo\}) \setminus  \dom  (suscritos \rres  \{Suspend\})\\
  rep! = ok
\end{schema}

\begin{schema}{SistSuspendIdle}
  \Delta SISTEMA\\
  rep!: MSG
\where
  \dom  (ps \rres  \{activo\}) \setminus  \dom  (suscritos \rres  \{Suspend\}) = \emptyset\\
  suscritos' = suscritos\\
  ps' = ps \oplus  (\dom  (ps \rres  \{activo\}) \cross  \{pasivo\})\\
  prim' = idle\\
  rep! = ok
\end{schema}

\begin{schema}{SistKillNowOK}
  \Delta SISTEMA\\
  rep!: MSG
\where
  \dom  (ps \rres  \{activo\}) \setminus  \dom  (suscritos \rres  \{KillNow\}) \neq  \emptyset\\
  suscritos' = suscritos\\
  ps' = ps \oplus  (\dom  (suscritos \rres  \{KillNow\}) \cap  \dom  (ps \rres  \{activo\}) \cross  \{muerto\})\\
  prim' \in  \dom  (ps \rres  \{activo\}) \setminus  \dom  (suscritos \rres  \{KillNow\})\\
  rep! = ok
\end{schema}

\begin{schema}{SistKillNowIdle}
  \Delta SISTEMA\\
  rep!: MSG
\where
  \dom  (ps \rres  \{activo\}) \setminus  \dom  (suscritos \rres  \{KillNow\}) = \emptyset\\
  suscritos' = suscritos\\
  ps' = ps \oplus  (\dom  (ps \rres  \{activo\}) \cross  \{muerto\})\\
  prim' = idle\\
  rep! = ok
\end{schema}

\begin{schema}{SistKill}
  \Delta SISTEMA\\
  rep!: MSG
\where
  suscritos' = suscritos\\
  ps' = ps \oplus  (\dom  (suscritos \rres  \{Kill\}) \cap  \dom  (ps \rres  \{pasivo\}) \cross  \{muerto\})\\
  prim' = prim\\
  rep! = ok
\end{schema}

\begin{schema}{Inv1}
  SISTEMA
\where
  prim = idle \lor  prim \in  \dom  (ps \rres  \{activo\})
\end{schema}

\begin{zed}
SistNuevoProceso == SistNuevoProcesoOK \lor  SistProcesoExistenteERR
\end{zed}

\begin{zed}
SistSuscProceso == SistSuscProcesoOK \lor  SistProcesoNoExistenteERR
\end{zed}

\begin{zed}
SistActivate == SistActivateOK \lor  SistActivateSC
\end{zed}

\begin{zed}
SistSuspend == SistSuspendOK \lor  SistSuspendIdle
\end{zed}

\begin{zed}
SistKillNow == SistKillNowOK \lor  SistKillNowIdle
\end{zed}


